\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2015-09-22 overview.tex
some fixes

\item The environment of the system must be modeled using \psharp. \psharp offers APIs for obtaining non-deterministically chosen values, which can be used to simulate failures, timers, etc. (see \S\ref{sec:method:driver}). This step captures external sources of nondeterminism. \psharp's testing engine can then systematically explore all choices, enumerating different asynchronous event interleavings, possible points of failures, timers firing, etc. (see \S\ref{sec:psharp:testing}).

>>>>

\item The environment of the system must be modeled in \psharp, which offers APIs for obtaining non-deterministically chosen values. These values can be used to simulate failures, timers, etc. (see \S\ref{sec:method:timer} and \S\ref{sec:method:driver}). This step captures external sources of nondeterminism. The \psharp testing engine can then systematically explore all choices, enumerating different asynchronous event interleavings, possible points of failures, timers firing, etc. (see \S\ref{sec:psharp:testing}).

### 2015-09-22 related.tex
some fixes

Tools such as CrystalBall~\cite{yabandeh2009crystalball} and \textsc{DeMeter}~\cite{guo2011practical} employ techniques based on dynamic partial order reduction~\cite{lauterburg2010evaluating} to reduce the exploration state-space. The SAMC~\cite{leesatapornwongsa2014samc} model checker offers a way of incorporating application-specific information during systematic testing to reduce the set of interleavings that they explore. These techniques are complementary to our approach: \psharp's systematic testing engine could use them for reducing the number of iterations it explores, just as the other tools can use language technnology (like \psharp) to write models and reduce the complexity of the system under test.

@@

Another formal approach is Verdi~\cite{wilcox2015verdi}, a framework for writing and verifying distributed systems in Coq~\cite{barras1997coq}. Verdi generates OCaml code from the verifying system, which can be used for execution. In contrast, \psharp performs bounded testing on a system already written in \csharp, which in our experience lowers the bar for adoption by product groups. Furthermore, Verdi does not currently support detecting liveness property violations, an important class of bugs in distributed storage systems.

>>>>

Tools such as CrystalBall~\cite{yabandeh2009crystalball} and \textsc{DeMeter}~\cite{guo2011practical} employ techniques based on dynamic partial order reduction~\cite{lauterburg2010evaluating} to reduce the exploration state-space. The SAMC~\cite{leesatapornwongsa2014samc} model checker offers a way of incorporating application-specific information during systematic testing to reduce the set of interleavings that the tool has to explore. These techniques are complementary to our approach: the \psharp systematic testing engine could use them for reducing the number of interleavings it explores, just as the other tools can use language technology (like \psharp) to write models and reduce the complexity of the system-under-test.

@@

Another formal approach is Verdi~\cite{wilcox2015verdi}, a framework for writing and verifying distributed systems in Coq~\cite{barras1997coq}. Verdi generates OCaml code from the verifying system, which can be used for execution. In contrast, \psharp performs bounded testing on a system already written in \csharp, which in our experience lowers the bar for adoption by engineering teams. Verdi does not currently support detecting liveness property violations, an important class of bugs in distributed storage systems.
